---
title: "Check coverage"
author: "Tim"
date: "July 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Check coverage of marine species that have any threat ascribed to them and check for accuracy against IUCN website. 

```{r}
dir_data <- "../data"
marine_species <- read.csv(file.path(dir_data, "spp_marine_from_api_2018-1.csv"))
iucn_species <- read.csv(file.path(dir_data, "iucn_species_list.csv")) 
risk_codes <- read.csv(file.path(dir_data, "risk_code_lookup.csv")) %>% dplyr::select(code, code_current)
colnames(iucn_species) <- gsub(colnames(iucn_species), pattern="result\\.", replacement="")
marine_species <- marine_species %>% 
  left_join(iucn_species, by=c("iucn_sid"="taxonid")) %>% 
  left_join(risk_codes, by=c("category"="code")) %>% 
  mutate(category=code_current) %>% 
  dplyr::select(-code_current)
#spp_ids <- marine_species %>% pull(iucn_sid) %>% unique()

marine_species %>% 
  ggplot(aes(x=category)) +
  geom_bar()

species_threats <- read.csv(file.path(dir_data, "species_threats.csv"))
species_with_threats <- marine_species %>% filter(scientific_name %in% unique(species_threats$name))
species_with_threats %>% 
  ggplot(aes(x=category)) +
  geom_bar()

species_without_threats <- marine_species %>% 
  filter(!scientific_name %in% unique(species_threats$name))

species_without_threats %>% 
  ggplot(aes(x=category)) +
  geom_bar()


```
After reviewing this, it seems that I should not restrict my analysis to species with fishing as a threat as it depends on the classification. 
Species of least concern can have threats attributed to them. 




```{r}
species_fishing_threats <- read.csv(file.path(dir_data, "species_fishing_threats.csv"))
species_threats_narrative <- read.csv(file.path(dir_data, "species_threats_narrative.csv"))
narrative_threats_output <- read.csv(file.path(dir_data, "narrative_threats_output.csv"))

```


Things to fix in API:
- some species did not return results from first attempt (e.g., Acanthurus mata)

Spatial API:
- Incorporate accessing of maps from species not available for download
- 

