---
title: "gear_price_estimator"
author: "Tim"
date: "August 12, 2019"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message=F, warning=F)
source("../R/common_fxns.R")
packages <- c("tidyverse")
ipak(packages)
dir_data <- "../data"
```

Objective: To extrapolate from known relationships of gear as a determinant of price to produce multipliers for the FERU ex-vessel price database. 

References:


Data Sources:
UK Fleet Landings - https://www.gov.uk/government/statistical-data-sets/uk-fleet-landings-and-foreign-fleet-landings-into-the-uk-by-port
Compiled here: https://www.kaggle.com/theflyingmunkey/uk-fleet-landings


NMFS - https://www.st.nmfs.noaa.gov/commercial-fisheries/commercial-landings/landings-by-gear/index
Query information: 'ALL SPECIES INDIVIDUALLY', 2000-2016; All States; ALL GEAR INDIVIDUALLY; DOWNLOAD ASCII FILE - PC
The query information must be removed from the output file before the file can be loaded into R correctly. 

```{r data}
nmfs <- read_csv(file.path(dir_data, "MF_GEAR_LANDINGS.txt"))
colnames(nmfs)[4:6] <- c("Tonnes", "Pounds", "Value")
nmfs <- nmfs %>% 
  filter(Pounds >0) %>% 
  filter(Value > 0) %>% 
  mutate(Tonnes = Pounds/ 2204.623) %>% 
  mutate(Price=Value/Tonnes) %>% 
  mutate(Country="USA")

uk <- data.table::fread(file.path(dir_data, "UK_fleet_landings_cleaned_kaggle.csv"))
uk <- uk %>% 
  rename(Year = year, 
         gear_type = gear_category,
         Tonnes = live_weight,
         Value = value_gbp,
         Species=species) %>%
  filter(Tonnes >0) %>% 
  filter(Value > 0) %>% 
  mutate(Price=Value/Tonnes) %>% 
  mutate(Country="UK")

nmfs_species_names <- data.table::fread(file.path(dir_data, "US_Common_Names.csv"))
nmfs_species_names <- nmfs_species_names %>% mutate(Name = str_to_lower(Name))
asfis <- data.table::fread(file.path(dir_data, "ASFIS_sp_2019.txt")) %>% mutate(English_name = str_to_lower(English_name))

us_gear_table <- read_csv(file.path(dir_data, "US_Gear.csv"))
uk_gear_table <- read_csv(file.path(dir_data, "UK_Gear.csv"))

```


```{r cleaning}

nmfs <- nmfs %>% left_join(us_gear_table)
nmfs <- nmfs %>% mutate(Species= str_to_lower(Species)) %>% left_join(nmfs_species_names, by=c("Species"="Name"))
nmfs %>% filter(is.na(SciName)) %>% pull(Species) %>% unique()


nmfs <- nmfs %>% mutate(Species = str_to_lower(Species))
nmfs <- nmfs %>% 
  mutate(PreNom = gsub(Species, pattern= ".*, ", replacement=""),
         SurNom = gsub(Species, pattern=", .*", replacement="")) %>% 
  mutate(CommonName = if_else(PreNom==SurNom, PreNom, paste(PreNom, SurNom)))
nmfs <- nmfs %>% left_join(asfis, by=c("CommonName"="English_name"))
nmfs %>%  filter(is.na(Scientific_name)) %>% pull(Species) %>% unique()

nmfs <- nmfs %>% dplyr::select(Year, Species, super_code, Country, Price, Tonnes)
uk <- uk %>% left_join(uk_gear_table) %>% dplyr::select(Year, Species, super_code, Country, Price, Tonnes)

model_data <- bind_rows(nmfs, uk)

#Set reference case:
model_data <- model_data %>% 
  mutate(super_code = fct_relevel(super_code, "bottom trawl", after=0)) %>% 
  mutate(Species = str_to_lower(Species))

#unique(model_data$Species)
```


```{r modeling}
mod <- lfe::felm(log(Price) ~ super_code + Species + Year + Country + log(Tonnes),
                 data=model_data)

plot(model_data$Year, mod$residuals)

```


```{r clean-output}
output_raw <- broom::tidy(mod)
output_raw <- output_raw %>% 
  filter(grepl(term, pattern="super_code")) %>% 
  mutate(term = gsub(term, pattern="super_code", replacement="")) %>% 
  rename(super_code=term)

missing_gear_types <- gear_table %>% pull(super_code) %>% unique()
missing_gear_types <- missing_gear_types[!missing_gear_types %in% output_raw$super_code]

missing_cases <- tibble(super_code= missing_gear_types, 
       estimate=rep(0, length(missing_gear_types)),
       std.error=rep(0, length(missing_gear_types)),
       statistic=rep(0, length(missing_gear_types)),
       p.value=rep(0, length(missing_gear_types)))

output_raw <- output_raw %>% 
  bind_rows(missing_cases)
```


```{r output}
output <- output_raw
output <- output %>% 
  mutate(multiplier_mean = exp(estimate)) %>% 
  mutate(multiplier_ll = exp(estimate) - (1.96*std.error),
         multiplier_ul = exp(estimate) + (1.96*std.error))
write_csv(output, file.path(dir_data, "gear_price_multipliers.csv"))

```

