---
title: "IUCN_API"
author: "Tim"
date: "August 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
packages <- c("tidyverse", 
              "jsonlite", 
              "httr",
              "parallel",
              "jsonlite",
              "RPushbullet")
ipak(packages)
dir_data <- "../data"


```

# API Data extraction from IUCN Red List
Token: (Authorized to Tim Cashion, trcashion@gmail.com)
Reference doc: http://apiv3.iucnredlist.org/api/v3/docs
Get all species by comprehensive group: 
/api/v3/comp-group/getspecies/:group?token='YOUR TOKEN'
Global assessment threats; /api/v3/threats/species/name/:name?token='YOUR TOKEN'
Regional assessment threats; /api/v3/threats/species/:name/region/:region_identifier?token='YOUR TOKEN'
Global threat output example (token is example token from IUCN): 
http://apiv3.iucnredlist.org/api/v3/threats/species/name/Loxodonta%20africana?token=9bb4facb6d23f48efbf424bb05c0c1ef1cf6f468393bc745d42179ac4aca5fee
{"name":"Loxodonta africana","result":[{"code":"1.1","title":"Housing & urban areas","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"11.2","title":"Droughts","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"1.2","title":"Commercial & industrial areas","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.1","title":"Annual & perennial non-timber crops","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.1.1","title":"Shifting agriculture","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.1.2","title":"Small-holder farming","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.1.3","title":"Agro-industry farming","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.2","title":"Wood & pulp plantations","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.2.1","title":"Small-holder plantations","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.2.2","title":"Agro-industry plantations","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.3","title":"Livestock farming & ranching","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.3.1","title":"Nomadic grazing","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.3.2","title":"Small-holder grazing, ranching or farming","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"2.3.3","title":"Agro-industry grazing, ranching or farming","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"4.1","title":"Roads & railroads","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.1","title":"Hunting & trapping terrestrial animals","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.1.1","title":"Intentional use (species is the target)","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.1.2","title":"Unintentional effects (species is not the target)","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.1.3","title":"Persecution/control","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.3","title":"Logging & wood harvesting","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"5.3.5","title":"Motivation Unknown/Unrecorded","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"6.1","title":"Recreational activities","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"6.2","title":"War, civil unrest & military exercises","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"7.1","title":"Fire & fire suppression","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"7.1.3","title":"Trend Unknown/Unrecorded","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"7.2","title":"Dams & water management/use","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"7.2.11","title":"Dams (size unknown)","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"8.1","title":"Invasive non-native/alien species/diseases","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null},{"code":"8.1.1","title":"Unspecified species","timing":"Ongoing","scope":null,"severity":null,"score":"Low Impact: 3","invasive":null}]}

```{r}
my_token <- read_file("../IUCN_token.txt") 
version <- paste("version_", fromJSON(content(GET(url = "http://apiv3.iucnredlist.org/api/v3/version"), "text"), flatten=TRUE)[[1]], sep="")
reload <- if_else(version=="version_2019-2", FALSE, TRUE)
reload <- FALSE
```

Establish full IUCN species list
```{r}
####Establish species lists ####
if(reload==TRUE){
  page_numbers <- seq(0,10, 1) #New IUCN data extends past 100,000 species. Updated to include 10 pages. #Modify this so it updates automatically.
  full_species_list <- tibble()
  for (number in page_numbers){
    species_url = paste("http://apiv3.iucnredlist.org/api/v3/species/page/", number,"?token=", my_token, sep="")
    species_request <- GET(url = species_url)
    species_text <- content(species_request, "text")
    species_text_flat <- fromJSON(species_text, flatten = TRUE)
    species_text_df <- as.data.frame(species_text_flat)
    species_text_df <- species_text_df %>% 
      mutate(page= as.character(page))
    full_species_list <- bind_rows(full_species_list, species_text_df)
  }
  write_csv(full_species_list, file.path(dir_data, paste("iucn_species_list_", version,".csv", sep="")))
}

```

Establish which are Marine species based on their habitat and listed system. Some species that are listed as 'marine' are only incidentally marine. 
```{r}
#Determine marine species list: Adapted from O'Hara, 2019

#based on system 
full_species_list <- data.table::fread(file.path(dir_data, paste("iucn_species_list_", version,".csv", sep="")))
full_species_ids <- full_species_list %>% pull(result.taxonid)
i <- 0
species <- full_species_ids[1]
species_systems <- tibble()

if(reload==FALSE){
  species_systems <- read.csv(file.path(dir_data, paste("species_systems.csv")), colClasses = "character")
  full_species_ids <- full_species_ids[!full_species_ids %in% species_systems$result.taxonid]
}

pbPost("note", "IUCN Systems code", body="Species systems finished")

for (species in full_species_ids){
  i <- i+1
  Sys.sleep(1.5)
  species_url = paste("http://apiv3.iucnredlist.org/api/v3/species/id/", species,"?token=", my_token, sep="")
  species_request <- GET(url = species_url)
  species_text <- content(species_request, "text")
  species_text_flat <- fromJSON(species_text, flatten = TRUE)
  if(length(species_text_flat$result)>0){
    species_text_df <- as.data.frame(species_text_flat) %>% mutate_all(as.character) 
    species_text_df <- species_text_df %>% select( c(result.taxonid, grep(colnames(species_text_df), pattern="system")))
    species_systems <- bind_rows(species_systems, species_text_df)
    print(paste("Retrieved new information for ", species, sep=""))
  }
  msg <- paste(i, "of ", length(full_species_ids), "completed")
  print(msg)
}
write_csv(species_systems, file.path(dir_data, paste("species_systems.csv")))
pbPost("note", "IUCN Systems code", body=msg)
#based on habitats
full_species_list <- data.table::fread(file.path(dir_data, paste("iucn_species_list_", version,".csv", sep="")))
species_systems <- data.table::fread(file.path(dir_data, paste("species_systems.csv")))
#Filter out species not found in marine or freshwater 
marine_freshwater_species <- species_systems %>% filter(result.marine_system==T|result.freshwater_system==T)
marine_species <- species_systems %>% filter(result.marine_system==T)

full_species_list <- full_species_list %>% filter(result.taxonid %in% marine_species$result.taxonid)
full_species_ids <- full_species_list %>% pull(result.taxonid)

pbPost("note", "IUCN Systems code", body="Species habitat API finished")

i <- 0
species <- full_species_ids[1]
species_habitats <- tibble()
if(reload==FALSE){
  species_habitats <- read.csv(file.path(dir_data, paste("species_habitats.csv")), colClasses = "character")
  full_species_ids <- full_species_ids[!full_species_ids %in% species_habitats$id]
  full_species_ids <- full_species_ids[!full_species_ids %in% species_habitats$result.code]
}


for (species in full_species_ids){
    i <- i+1
    Sys.sleep(1.5)
    species_url = paste("http://apiv3.iucnredlist.org/api/v3/habitats/species/id/", species,"?token=", my_token, sep="")
    species_request <- GET(url = species_url)
    species_text <- content(species_request, "text")
    species_text_flat <- fromJSON(species_text, flatten = TRUE)
    if(length(species_text_flat$result)>0){
      species_text_df <- as.data.frame(species_text_flat) %>% mutate_all(as.character)
      species_habitats <- bind_rows(species_habitats, species_text_df)
      print(paste("Retrieved new information for ", species, sep=""))
    }
    print(paste(i, "of ", length(full_species_ids), "completed"))
    }

write_csv(species_habitats, file.path(dir_data, paste("species_habitats.csv")))
pbPost("note", "IUCN Systems code", body="Species habitat code stopped.")


full_species_list <- data.table::fread(file.path(dir_data, paste("iucn_species_list_", version,".csv", sep="")), colClasses = "character")
iucn_habitat <- read.csv(file.path(dir_data, "iucn_habitat_categories.csv"), colClasses = "character")
iucn_habitat <- iucn_habitat %>% filter(include==TRUE)
iucn_habitat <- iucn_habitat %>% 
  mutate(max_depth = case_when(all((cat == 10 & subcat1 %in% 3:4) |
                            cat == 11)        ~ 'deep oceanic',
                      any(cat %in% c(10, 11)) ~ '200 m +',
                      any(cat %in% c(9, 15))  ~ '< 200 m',
                      any(cat %in% c(12))     ~ '< 20 m',
                      TRUE                    ~ 'unknown'))
iucn_habitat <- iucn_habitat %>% 
  mutate(max_depth = if_else((cat==10 & subcat1 %in% c(3,4))|cat==11, "deep oceanic", 
                             if_else(cat %in% c(10,11), "200 m +", 
                                     if_else(cat %in% c(9,15), "< 200 m", 
                                             if_else(cat %in% c(12), "< 20 m", "unknown"))))
         )


species_habitats <- data.table::fread(file.path(dir_data, paste("species_habitats.csv")), colClasses = "character")
species_systems <- data.table::fread(file.path(dir_data, paste("species_systems.csv")), colClasses = "character")

habitat_info <- species_habitats %>%left_join(iucn_habitat, by=c("result.code"="code")) %>% left_join(species_systems, by=c("id"="result.taxonid"))

full_species_list <- full_species_list %>% left_join(habitat_info, by=c("result.taxonid"="id"))

marine_species <- full_species_list %>% filter(result.code %in% iucn_habitat$code | result.marine_system==TRUE)

marg_suit <- full_species_list %>%
  group_by(result.taxonid) %>%
  filter(result.code %in% iucn_habitat$code) %>%
  arrange(result.suitability) %>%
  summarize(suit_all = tolower(paste0(unique(result.suitability), collapse = ', ')) ,
            intertidal_only = sum(!cat %in% c(12) & !(cat == 9 & subcat1 == 10)) == 0) %>%
  ### cat 9.10 is estuaries - if only intertidal or estuaries, 
  ### check for suitability
  left_join(data.table::fread(file.path(dir_data, paste("iucn_species_list_", version,".csv", sep="")), colClasses = "character"), by = 'result.taxonid') %>%
  filter(!str_detect(suit_all, 'suitable|unknown|^na')) %>%
  filter(intertidal_only) %>%
  select(result.taxonid, result.scientific_name, result.kingdom_name, result.phylum_name, result.class_name, result.order_name, result.family_name)

#Filter out marginal species 
marine_species_clean <- marine_species %>%
  rename(iucn_sid = result.taxonid) %>% 
  filter(!iucn_sid %in% marg_suit$result.taxonid) %>%
  group_by(iucn_sid, max_depth) %>%
  summarize(habs = paste0(result.code, collapse = ', '))

write_csv(marine_species_clean, file.path(dir_data,
                                    paste('spp_marine_from_', version, ".csv", sep="")))



```

Regional assessments
```{r}
#### Get regional assessments####
marine_species <- read.csv("./data/spp_marine_from_api_2018-1.csv")


regions_response <- GET(url= paste("http://apiv3.iucnredlist.org/api/v3/region/list?token=", my_token, sep=""))
regions <- as.data.frame(fromJSON(content(regions_response, "text"), flatten=TRUE))
regions_list <- regions$results.identifier
regions_list <- regions_list[regions_list!="global"]

# region <- regions_list[1]
regional_assessments <- tibble()
for (region in regions_list){
  number <- 0
  regions_response <- GET(url= paste("http://apiv3.iucnredlist.org/api/v3/species/region/",region ,"/page/",number, "?token=", my_token, sep=""))
  regions <- as.data.frame(fromJSON(content(regions_response, "text"), flatten=TRUE))
  #regions_list <- regions$results.identifier
  regional_assessments <- regional_assessments %>% bind_rows(regions)
  if(regions$count[1]==10000){
    number <- 1
    regions_response <- GET(url= paste("http://apiv3.iucnredlist.org/api/v3/species/region/",region ,"/page/",number, "?token=", my_token, sep=""))
    regions <- as.data.frame(fromJSON(content(regions_response, "text"), flatten=TRUE))
    #regions_list <- regions$results.identifier
    regional_assessments <- regional_assessments %>% bind_rows(regions)
  }
}

write.csv(regional_assessments, file.path(dir_data, "regional_assessments.csv"))
marine_regional_assessments <- regional_assessments %>% filter(result.taxonid %in% marine_species$iucn_sid)
write.csv(marine_regional_assessments, file.path(dir_data, "marine_regional_assessments.csv"))

```

Identify species with 'fishing' as a threat (category 5.4)

```{r}
#Use marine species list as established from habit types.
#Habitat type information retrieved from https://github.com/oharac/spp_risk_dists from O'Hara et al. 2019. 

full_species_list <- read_csv(file.path(dir_data, "iucn_species_list.csv"))
marine_species <- read.csv(file.path(dir_data, paste("spp_marine_from_", version, ".csv", sep="")))

marine_species_df <- full_species_list %>% 
  filter(result.taxonid %in% marine_species$iucn_sid) %>% 
  mutate(result.scientific_name = as.character(result.scientific_name))
marine_species_list <- full_species_list %>% 
  filter(result.taxonid %in% marine_species$iucn_sid)

#Fixing species_threats after switching to ID
# species_threats <- read.csv("./data/species_threats.csv", stringsAsFactors = FALSE)
# species_threats_name <- species_threats %>% filter(is.na(id)) %>% dplyr::select(-id)
# species_threats_name <- species_threats_name %>% 
#   left_join(marine_species_df %>% dplyr::select(result.taxonid, result.scientific_name), 
#                                                            by=c("name"="result.scientific_name")) %>% 
#   rename(id=result.taxonid) %>% 
#   dplyr::select(-name)
# species_threats_id <- species_threats %>% filter(is.na(id)==F) %>% dplyr::select(-name)
# species_threats <- bind_rows(species_threats_name, species_threats_id)
# write_csv(species_threats, "./data/species_threats.csv")
#### Get identified threats from codes ####
species_threats <- tibble()
if(reload==FALSE){
  species_threats <- read.csv(file.path(dir_data, "species_threats.csv"), stringsAsFactors = FALSE) %>% mutate(id=as.character(id))
  completed_species <- unique(species_threats$id)
  marine_species_list <- marine_species_list %>% filter(!result.taxonid %in% completed_species)
}
marine_species_list <- marine_species_list %>% pull(result.taxonid)
i <- 0
for (species in marine_species_list){
  i <- i+1
  Sys.sleep(1)
  species_url = paste("http://apiv3.iucnredlist.org/api/v3/threats/species/id/", species,"?token=", my_token, sep="")
  species_request <- GET(url = species_url)
  species_text <- content(species_request, "text")
  species_text_flat <- fromJSON(species_text, flatten = TRUE)
  if(length(species_text_flat$result)>0){
    species_text_df <- as.data.frame(species_text_flat) %>% mutate_all(as.character)
    species_threats <- bind_rows(species_threats, species_text_df)
    print(paste("Retrieved new information for ", species, sep=""))
  }
  print(paste(i, "of ", length(marine_species_list), "completed"))
}
species_threats <- species_threats %>% unique()
species_threats$name <- str_to_sentence(species_threats$name)
write_csv(species_threats, "./data/species_threats.csv")

fishing_threats <- c("5.4","5.4.1","5.4.2","5.4.3", "5.4.4")
species_threats_df <- species_threats %>% 
  filter(code %in% fishing_threats)
  #filter(result.code %in% fishing_threats) %>%
  #rename(result.scientific_name = name)
species_fishing_threats <- left_join(species_threats_df, marine_species_df, by=c("iucn_sid" = "result.taxonid"))
#species_fishing_threats <- left_join(species_threats_df, marine_species_df, by="result.scientific_name")

write_csv(species_fishing_threats, "./data/species_fishing_threats.csv")

```

Identify gear types in 'narrative text'. This text is taken from the 'Threats in Detail' and 'Trade and Use' sections of each species page.
```{r }
#### Get identified threats from narrative ####
marine_species_fishing_list <- read_csv(file.path(dir_data, "species_fishing_threats.csv"))

if(reload==FALSE){
  species_threats_narrative <- read_csv(file.path(dir_data, "species_threats_narrative.csv"))
  marine_species_fishing_list <- marine_species_fishing_list %>% filter(!iucn_sid %in% species_threats_narrative$result.species_id) %>% unique()
  # marine_species_fishing_list <- marine_species_fishing_list %>% filter(!result.scientific_name %in% species_threats_narrative$name) %>% unique()
} else {
  species_threats_narrative <- tibble()
}
marine_species_fishing_list <- marine_species_fishing_list %>% pull(iucn_sid) %>% unique()
#marine_species_fishing_list <- marine_species %>% pull(iucn_sid) %>% unique()

i <- 0
for (species in marine_species_fishing_list){
  i <- i+1
  Sys.sleep(3)
  species_url = paste("http://apiv3.iucnredlist.org/api/v3/species/narrative/id/", species,"?token=", my_token, sep="")
  species_request <- GET(url = species_url)
  species_text <- content(species_request, "text")
  species_text_flat <- fromJSON(species_text, flatten = TRUE)
  if(length(species_text_flat$result)>0){
    species_text_df <- as.data.frame(species_text_flat)
    species_text_df <- species_text_df %>% 
      dplyr::select(name, result.species_id, result.threats, result.usetrade) %>% 
      mutate(iucn_id = result.species_id,
             name = as.character(name),
             result.threats = as.character(result.threats),
             result.usetrade = as.character(result.usetrade))
    species_threats_narrative <- bind_rows(species_threats_narrative, species_text_df)
    print(paste(i, "of ", length(marine_species_fishing_list), "completed"))
  }else {
    print(paste("No narrative text for species", species))
  }
}
write_csv(species_threats_narrative, file.path(dir_data, "species_threats_narrative.csv"))


#### Get identified threats from narrative for non-fishing threatened species####
marine_species <- read.csv(file.path(dir_data, paste("spp_marine_from_", version, ".csv", sep="")))
marine_species_nonfishing_list <- marine_species

if(reload==FALSE){
  species_threats_narrative <- read_csv(file.path(dir_data, "species_threats_narrative.csv"))
  species_nonfishing_narrative <- read_csv(file.path(dir_data, "species_nonfishing_threats_narrative.csv"))
  marine_species_nonfishing_list <- marine_species_nonfishing_list %>% filter(!iucn_sid %in% species_threats_narrative$result.species_id) %>% unique()
  marine_species_nonfishing_list <- marine_species_nonfishing_list %>% filter(!iucn_sid %in% species_nonfishing_narrative$iucn_id) %>% unique()
} else {
  species_threats_narrative <- tibble()
}
marine_species_nonfishing_list <- marine_species_nonfishing_list %>% pull(iucn_sid) %>% unique()
#marine_species_fishing_list <- marine_species %>% pull(iucn_sid) %>% unique()

i <- 0
for (species in marine_species_nonfishing_list){
  i <- i+1
  Sys.sleep(1)
  species_url = paste("http://apiv3.iucnredlist.org/api/v3/species/narrative/id/", species,"?token=", my_token, sep="")
  species_request <- GET(url = species_url)
  species_text <- content(species_request, "text")
  species_text_flat <- fromJSON(species_text, flatten = TRUE)
  if(length(species_text_flat$result)>0){
    species_text_df <- as.data.frame(species_text_flat)
    species_text_df <- species_text_df %>% 
      dplyr::select(result.species_id, result.threats, result.usetrade) %>% 
      mutate(iucn_id = result.species_id,
             #name = as.character(name),
             result.threats = as.character(result.threats),
             result.usetrade = as.character(result.usetrade)) %>% 
      dplyr::select(-result.species_id)
    species_nonfishing_narrative <- bind_rows(species_nonfishing_narrative, species_text_df)
    print(paste(i, "of ", length(marine_species_nonfishing_list), "completed"))
  }else {
    print(paste("No narrative text for species", species))
  }
}
species_nonfishing_narrative <- species_nonfishing_narrative %>% distinct()
write_csv(species_nonfishing_narrative, file.path(dir_data, "species_nonfishing_threats_narrative.csv"))

```

Regional threats and uses
```{r}
for (species in marine_species_fishing_list){
  i <- i+1
  Sys.sleep(3)
  species_url = paste("http://apiv3.iucnredlist.org//api/v3/species/id/", species, "/region/", region,"?token=", my_token, sep="")
  species_request <- GET(url = species_url)
  species_text <- content(species_request, "text")
  species_text_flat <- fromJSON(species_text, flatten = TRUE)
  species_text_df <- as.data.frame(species_text_flat)
  species_text_df <- species_text_df %>% 
    dplyr::select(name, result.species_id, result.threats, result.usetrade) %>% 
    mutate(iucn_id = result.species_id,
           name = as.character(name),
           result.threats = as.character(result.threats),
           result.usetrade = as.character(result.usetrade))
  species_threats_narrative <- bind_rows(species_threats_narrative, species_text_df)
  print(paste(i, "of ", length(marine_species_fishing_list), "completed"))
}
write_csv(regional_assessments, file.path(dir_data, "iucn_rgn_assessments.csv"))

```


Identify any remaining spatial files that would expand analysis. Currently, not available. 
```{r}
####Spatial Files needed####
full_species_list <- read_csv(file.path(dir_data,"iucn_species_list.csv"))
marine_species <- read.csv(file.path(dir_data, "spp_marine_from_", version, ".csv"))
dir_rasters <- "./spatial/spp_rasters"
species_fishing_threats <- read_csv(file.path(dir_data,"species_fishing_threats.csv"))

marine_species_df <- full_species_list %>% 
  filter(result.taxonid %in% marine_species$iucn_sid) %>% 
  mutate(result.scientific_name = as.character(result.scientific_name))
marine_species_list <- full_species_list %>% 
  filter(result.taxonid %in% marine_species$iucn_sid) %>% 
  dplyr::select(result.scientific_name)
spat_files <- list.files(file.path(paste(dir_o_raster, "_", cell_size, sep="")))
spat_files <- gsub(spat_files, pattern="iucn_sid_", replacement = "")
spat_files <- gsub(spat_files, pattern=".csv", replacement = "")
all_spat_needed <- marine_species %>% filter(!iucn_sid %in% spat_files) %>% pull(iucn_sid) %>% unique()
threat_spat_needed <- species_fishing_threats %>% filter(!result.taxonid %in% spat_files) %>% pull(result.taxonid) %>% unique() ###Files where I have fishing threats but no spatial data.


species_maps <- tibble()
i <- 0
for (species in threat_spat_needed){
  i <- i+1
  Sys.sleep(3)
  species_url = paste("http://apiv3.iucnredlist.org//api/v3/species/narrative/", species,"?token=", my_token, sep="")
  # species_request <- GET(url = species_url)
  # species_text <- content(species_request, "text")
  # species_text_flat <- fromJSON(species_text, flatten = TRUE)
  # species_text_df <- as.data.frame(species_text_flat)
  # species_text_df <- species_text_df %>% 
  #   dplyr::select(name, result.species_id, result.threats, result.usetrade) %>% 
  #   mutate(iucn_id = result.species_id,
  #          name = as.character(name),
  #          result.threats = as.character(result.threats),
  #          result.usetrade = as.character(result.usetrade))
  # species_threats_narrative <- bind_rows(species_threats_narrative, species_text_df)
  print(paste(i, "of ", length(threat_spat_needed), "completed"))
}

```

