---
title: "profit estimation"
author: "Tim"
date: "August 12, 2019"
output: html_document
---

```{r setup, include=FALSE}

#knitr::opts_chunk$set(echo = FALSE, message=F, warning=F)
source("../R/common_fxns.R")
packages <- c("tidyverse")
ipak(packages)
dir_data <- "../data"
dir_spatial_csvs <- "../spatial/csvs"
```

Objective: To determine profits by fishing gear type at a spatial scale. 

Dependencies:
- Cost of fishing database (Lam et al. 2011)
- Requires outputs of sau_data_processing.Rmd and gear_price_estimator.Rmd

Steps:
1) Adjust prices by gear type to derive new price
2) Estimate revenue by gear type for each for each country
3) Estimate profit by matching each country's gear type to their cost of fishing
4) Output clean version of profit by cell_id without country information. 

```{r raw-data}
sau_df <- data.table::fread(file.path(dir_data, "sau_catch_value_country.csv"))
gear_price_multiplier <- read_csv(file.path(dir_data, "gear_price_multipliers.csv"))
cost_of_fishing <- read_csv(file.path(dir_data, "cost_of_fishing_database.csv"))
fe_ids <- read_csv(file.path(dir_data, "fishing_entity_ids.csv"))
fao_region_fe_ids <- read_csv(file.path(dir_data, "fao_region_fishing_entity_ids.csv"))
cell_ids <- read_csv(file.path(dir_spatial_csvs, "cell_ids.txt"), col_names = c("cell_id", "lon", "lat"))
gear_table <- read_csv(file.path(dir_data, "sau_gear_table.csv"))
feru_gear_table <- read_csv(file.path(dir_data, "feru_gear_table.csv"))
```


```{r cleaning}

#Clean combined Sea Around Us data
sau_df <- sau_df %>% 
  mutate(value = ifelse(value==0, catch*1496, value))
sau_df <- sau_df %>% 
  mutate(price = value/catch)
sau_df <- sau_df %>% left_join(gear_table, by=c("gear_type_id" = "gear_id")) %>% left_join(gear_price_multiplier)
sau_df <- sau_df %>% 
  mutate(new_price_mean = price * multiplier_mean,
         new_price_ll = price * multiplier_ll,
         new_price_ul = price * multiplier_ul) %>% 
  mutate(value = new_price_mean * catch)


regional_average_gear_costs <- cost_of_fishing %>% 
  left_join(feru_gear_table) %>% 
  group_by(FAORegion, super_code) %>% 
  summarize(AverageCost= mean(`TotCost (US$ per tonne of catch in 2005 real dollar)`)) 

regional_average_costs <- cost_of_fishing %>% 
  left_join(feru_gear_table) %>% 
  group_by(FAORegion) %>% 
  summarize(RegionalAverageCost= mean(`TotCost (US$ per tonne of catch in 2005 real dollar)`)) 



#Need to add in 'unknown' classes and small scale where it isn't found in the data. 

regional_costs <- expand.grid(FAORegion=unique(regional_average_gear_costs$FAORegion), super_code=c(unique(regional_average_gear_costs$super_code), "unknown"))
regional_costs <- regional_costs %>% 
  left_join(regional_average_gear_costs) %>% 
  left_join(regional_average_costs) %>% 
  mutate(AverageCost = ifelse(is.na(AverageCost), RegionalAverageCost, AverageCost)) %>% 
  left_join(fao_region_fe_ids)


#Clean cost of fishing database to match SAU data 
cost_of_fishing <- cost_of_fishing %>% 
  left_join(feru_gear_table) %>% 
  dplyr::select(Country, super_code, `TotCost (US$ per tonne of catch in 2005 real dollar)`) %>% 
  rename(fishing_entity=Country,
         total_cost = `TotCost (US$ per tonne of catch in 2005 real dollar)`) %>% 
  left_join(fe_ids) %>% 
  group_by(fishing_entity_id, super_code) %>% 
  summarize(total_cost=mean(total_cost))

  
  
```


```{r modeling}
df <- sau_df %>% 
  left_join(cost_of_fishing) %>% 
  left_join(cell_ids) 


#Check missing data:
# df %>% filter(is.na(value))
# df %>% filter(is.na(cost)) %>% pull(super_code) %>% unique()


df <- df %>% 
  left_join(regional_costs)
df <- df %>% 
  mutate(cost_to_use = if_else(is.na(total_cost), AverageCost, total_cost))

df <- df %>% 
  mutate(cost = cost_to_use*catch) %>% 
  mutate(profit = value-cost)

# df %>% filter(is.na(cost))
# df %>% filter(is.nan(profit))

hist(log(df$profit))
```


```{r clean-output}
output <- df %>% 
  group_by(super_code, lon, lat, year) %>%
  summarize(catch=sum(catch),
            profit=sum(profit)) %>%
  ungroup() %>%
  group_by(super_code, lon, lat) %>%
  summarize(mean_catch = mean(catch),
            mean_profit = mean(profit))

```


```{r output}
#output <- output_raw
write_csv(output, file.path(dir_data, "allocated_super_gear_profit.csv"))

```

